Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-09-01 Docs/Paper/LaTex/template.tex
minor corrections

The vZ architecture is shown in Fig.~\ref{vZ-Architecture}. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, vZ invokes OptSAT for arithmetic or MaxSAT for soft constraints. \textcolor{red}{Qual seria o ``box constraints''?} For box constraints using real values, Vz combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', vZ invokes MaxSAT using multiple calls for its engine. \textcolor{red}{Qual ``engine''?} 
%
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
	\caption{vZ Architecture~\cite{Bjorner2015}}
	\label{vZ-Architecture}
\end{figure}

@@

As computer hardware architecture moves from single- to multi-cores, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores. This section proposes two multi-core model checking algorithms in order to speed up the HW-SW partitioning verification if compared to the sequential solution.

%----------------------------------------------
\section{Verification Algorithm using Sequential ESBMC}
\label{Verification-Algorithm-using-ESBMC}
%----------------------------------------------

>>>>

The vZ architecture is shown in Fig.~\ref{vZ-Architecture}. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, vZ invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, Vz combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', vZ invokes MaxSAT using multiple calls for its engine. \textcolor{red}{Qual ``engine''?} 
%
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=95px]{Image/vzArch.png} 
	\caption{vZ Architecture~\cite{Bjorner2015}}
	\label{vZ-Architecture}
\end{figure}

@@

As computer hardware architecture moves from single- to multi-cores, parallel programming environments should be exploited to take advantage of the ability to run several threads on different processing cores. This section describes the verification algorithm using sequential ESBMC, followerd by three multi-core model checking algorithms, in order to speed up the HW-SW partitioning verification if compared to the sequential solution.

%----------------------------------------------
\subsection{Verification Algorithm using Sequential ESBMC}
\label{Verification-Algorithm-using-ESBMC}
%----------------------------------------------
